The benefits of prefetching for large-scale cloud-based neuroimaging analysis workflows

### 2021-10-04 paper/paper.tex
figure fix

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{figures/prefetch_diagram.pdf}
\end{center}
\caption{Prefetching vs sequential transfers (\sfs)}
%https://docs.google.com/drawings/d/1MV5dIdLyBrM_HJX-0jOsIKf90UD8wXE_G5Cnmd-mY-A/edit
\label{fig:prefetch}
\end{figure}

@@

Rolling Prefetch combines prefetching with data eviction. By evicting data post application processing, it ensures a reduced footprint on local storage. Rolling Prefetch consists of three threads: (1) the reading thread loads data blocks from local storage and marks them for eviction, (2) the prefetching thread transfers data blocks from cloud storage to local storage, and (3) the eviction threads deletes the blocks that have been marked for eviction.
% \valerie{cut read alg below}
% \begin{algorithm}
% \SetAlgoLined
%     \SetKwInOut{Input}{Input}
%     \SetKwInOut{Output}{Output}
%     \Input{$start$ the start position of the read;\\
%     $end$ the end position of the read;\\}
%     \Output{$output$ the file contents located between $start$ and $end$}

@@

%%tristan do i keep this if our model is just a theoretical eval? maybe it should be placed where the model
%% is instead?
\begin{table}
\caption{Measured latency and bandwidth obtained from reading files ranging from \SI{1}{\kibi\byte} to \SI{4}{\gibi\byte} on a t2.xLarge instance reading from an S3 bucket in the same region.}
\centering
\begin{tabular}{| c | c | c| }
\cline{2-3}
  \multicolumn{1}{c|}{}& S3 & memory \\ 
  \hline
 bandwidth (MB/s) & 91 & 2221 \\  
 latency (s) & 0.1 & $\num{1.6e-6}$ \\
 \hline
\end{tabular}

\label{table:benchmarks}
\end{table}

@@

\begin{figure}
\begin{center}
\includegraphics[height=160pt]{figures/filesize.pdf}
\setlength{\abovecaptionskip}{0pt}
\setlength{\belowcaptionskip}{-10pt}
\caption{Runtime performance of reading subsets of the HYDI dataset stored on Amazon S3 into Nibabel using \sfs and Rolling Prefetch on an Amazon EC2 t2.xlarge instance. Blocksize was set to \SI{64}{\mebi\byte} on both \sfs and
Rolling Prefetch. Prefetch cache consisted of \SI{2}{\gibi\byte} tmpfs storage.}
\label{fig:filesize}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{figures/parallel.pdf}
\setlength{\abovecaptionskip}{-10pt}
\setlength{\belowcaptionskip}{-10pt}
\caption{Runtime performance of reading subsets of the HYDI dataset stored on Amazon S3 into Nibabel in parallel using 4
\sfs and Rolling Prefetch processes. Blocksize was set to \SI{64}{\mebi\byte} on both \sfs and Rolling Prefetch.
Prefetch cache consisted of \SI{1}{\gibi\byte} tmpfs storage.}
\label{fig:parallel}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{figures/blocksize.pdf}
\setlength{\abovecaptionskip}{-10pt}
 \setlength{\belowcaptionskip}{-20pt}
\caption{Runtime performance of reading a \SI{6}{\gibi\byte} subset of the HYDI dataset stored on Amazon S3 into Nibabel using
\sfs and Rolling Prefetch with various block size configurations on an Amazon EC2 t2.xlarge instance. Prefetch cache consisted of  \SI{2}{\gibi\byte} tmpfs storage.}
\label{fig:blocksize}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{figures/speedup.pdf}
\setlength{\abovecaptionskip}{-10pt}
\setlength{\belowcaptionskip}{-8pt}
\caption{Rolling prefetch speedup of the neuroimaging use-cases (histogram and bundle recognition) in various conditions. Experiments varying instance type and number of files were only performed with the bundle recognition pipeline.} 
\label{fig:speedup}
\end{center}
\end{figure}

@@

>>>>

Since Rolling Prefetch is implemented as a layer atop \sfs, it can easily replace an existing call to S3Fs by calling \texttt{S3PrefetchFileSystem} instead of \texttt{S3FileSystem}.

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{figures/prefetch_diagram.pdf}
\end{center}
\caption{Prefetching vs sequential transfers (\sfs)}
%https://docs.google.com/drawings/d/1MV5dIdLyBrM_HJX-0jOsIKf90UD8wXE_G5Cnmd-mY-A/edit
\vspace{-1.5em}
\label{fig:prefetch}
\end{figure}

@@

Rolling Prefetch combines prefetching with data eviction. By evicting processed data, it ensures a reduced footprint on the local storage leveraged as cache
(e.g. tmpfs, SSD, HDD). Rolling Prefetch consists of three threads: (1) the reading thread loads data blocks from local storage and marks them for eviction, (2) the prefetching thread transfers data blocks from cloud storage to local storage, and (3) the eviction threads deletes the blocks that have been marked for eviction.
% \valerie{cut read alg below}
% \begin{algorithm}
% \SetAlgoLined
%     \SetKwInOut{Input}{Input}
%     \SetKwInOut{Output}{Output}
%     \Input{$start$ the start position of the read;\\
%     $end$ the end position of the read;\\}
%     \Output{$output$ the file contents located between $start$ and $end$}

@@

%%tristan do i keep this if our model is just a theoretical eval? maybe it should be placed where the model
%% is instead?
\begin{table}
\caption{Measured latency and bandwidth obtained from reading files ranging from \SI{1}{\kibi\byte} to \SI{4}{\gibi\byte} on a t2.xLarge instance reading from an S3 bucket in the same region.}
\centering
\begin{tabular}{| c | c | c| }
\cline{2-3}
  \multicolumn{1}{c|}{}& S3 & memory \\ 
  \hline
 bandwidth (MB/s) & 91 & 2221 \\  
 latency (s) & 0.1 & $\num{1.6e-6}$ \\
 \hline
\end{tabular}
\vspace{-1.5em}
\label{table:benchmarks}
\end{table}

@@

\begin{figure}
\begin{center}
    \vspace{-0.6em}
\includegraphics[height=160pt]{figures/filesize.pdf}
\setlength{\abovecaptionskip}{0pt}
\setlength{\belowcaptionskip}{-30pt}
\caption{Runtime performance of reading subsets of the HYDI dataset stored on Amazon S3 into Nibabel using \sfs and Rolling Prefetch on an Amazon EC2 t2.xlarge instance. Blocksize was set to \SI{64}{\mebi\byte} on both \sfs and
Rolling Prefetch. Prefetch cache consisted of \SI{2}{\gibi\byte} tmpfs storage.}
\vspace{-5.53em}
\label{fig:filesize}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{figures/parallel.pdf}
\setlength{\abovecaptionskip}{-10pt}
\setlength{\belowcaptionskip}{-10pt}
\caption{Runtime performance of reading subsets of the HYDI dataset stored on Amazon S3 into Nibabel in parallel using 4
\sfs and Rolling Prefetch processes. Blocksize was set to \SI{64}{\mebi\byte} on both \sfs and Rolling Prefetch.
Prefetch cache consisted of \SI{1}{\gibi\byte} tmpfs storage.}
\vspace{-5.5em}
\label{fig:parallel}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{figures/blocksize.pdf}
\setlength{\abovecaptionskip}{-10pt}
 \setlength{\belowcaptionskip}{-20pt}
\caption{Runtime performance of reading a \SI{6}{\gibi\byte} subset of the HYDI dataset stored on Amazon S3 into Nibabel using
\sfs and Rolling Prefetch with various block size configurations on an Amazon EC2 t2.xlarge instance. Prefetch cache consisted of  \SI{2}{\gibi\byte} tmpfs storage.}
\vspace{-1.5em}
\label{fig:blocksize}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{figures/speedup.pdf}
\setlength{\abovecaptionskip}{-10pt}
\setlength{\belowcaptionskip}{-8pt}
\caption{Rolling prefetch speedup of the neuroimaging use-cases (histogram and bundle recognition) in various conditions. Experiments varying instance type and number of files were only performed with the bundle recognition pipeline.} 
\vspace{-1.5em}
\label{fig:speedup}
\end{center}
\end{figure}

@@

While our results pertain to the applicability of Rolling Prefetch to neuroimaging, similar speedups can be expected from other kinds of sequential processing, such as standard text file processing like word count.
